Cluster Difference Imaging Photometric Survey. II. TOI~837: A Young Validated Planet in IC~2602

### 2020-08-06 paper/ms.tex
clean repo
update manuscript

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=.49\textwidth]{f2b.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Ground-based follow-up photometry.} The data were acquired
    using the 0.36$\,$m telescope at El Sauce and the 0.40$\,$m
    ASTEP400 telescop at Dome C.  Black points represent the
    measurements after binning at 10-minute intervals. The gray line
    is the model that best fits the combined TESS and ground-based
    data.  Red and blue lines show 2-$\sigma$ lower limits on the
    transit depths in the Cousins-R and Johnson-B bandpasses used to
    rule out specific false positive scenarios (see
    Section~\ref{subsec:colorphot}).
		\label{fig:groundphot}
	}
\end{figure}

@@

We opted for this approach rather than a joint fit of the photometry
and radial velocities because the RVs on their own did not show
evidence for a planetary signal.  Our preference for using only the
TESS data to derive the transit parameters was in our view justified
by the systematic uncertainties inherent to ground-based light curve
production, particularly in comparison star selection.  Our assumption
of a constant radius across all bandpasses was tested by independently
fitting each ground-based transit while letting the planetary radius
float (Section~\ref{subsec:colorphot}). The transit depths did not
significantly change between different bandpasses.

The posteriors from fitting the TESS data alone are given in
Table~\ref{tab:posterior}.  The condition for a grazing transit is
whether the impact parameter $b$ is below $1 - R_{\rm p}/R_\star$.
The relevant posterior probabilities are shown in
Figure~\ref{fig:subsetcorner}.  The transit is therefore either
grazing, or nearly grazing.  From experimenting with the priors, we
found that in the absence of a strong prior on the stellar density,
the inherent degeneracy between the impact parameter and
planet-to-star size ratio would have been much stronger.  In the
absence of precise information about the star, a larger fraction of
the posterior would therefore have been grazing.  However, our priors
on the stellar parameters from the cluster isochrone fit break this
degeneracy, enabling us to report two-sided limits on the
planet-to-star size ratio.

@@

While we have statistically validated that \tn\ is a planet, the
possibility that it could be a background eclipsing binary has not
been excluded with sufficient confidence to call the planet
``confirmed''.  The distinction is methodological.  Our calculations
have shown that at a population level we expect negligibly few BEBs
within $\approx0.3''$ of \tn\ to produce eclipses of the appropriate
shape across all bandpasses, with no observed secondary eclipse or
odd-even variations (Section~\ref{subsec:fpp}).  This statement is
tautologically ``validation'', but it is weaker than having data on
hand that conclusively rules in favor of the planetary interpretation.

>>>>

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=.48\textwidth]{f3.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Ground-based follow-up photometry.} The data were acquired
    using the 0.36$\,$m telescope at El Sauce and the 0.40$\,$m
    ASTEP400 telescop at Dome C.  Black points represent the
    measurements after binning at 10-minute intervals. The gray line
    is the model that best fits the combined TESS and ground-based
    data.  Red and blue lines show 2-$\sigma$ lower limits on the
    transit depths in the Cousins-R and Johnson-B bandpasses used to
    rule out specific false positive scenarios (see
    Section~\ref{subsec:colorphot}).
		\label{fig:groundphot}
	}
\end{figure}

@@

We opted for this approach rather than a joint fit of the photometry
and radial velocities because the RVs on their own did not show
evidence for a planetary signal.  Our preference for using only the
TESS data to derive the transit parameters was in our view justified
by the systematic uncertainties inherent to ground-based light curve
production, particularly in comparison star selection.  Our assumption
of a constant radius across all bandpasses was tested by independently
fitting each ground-based transit while letting the planetary radius
float (Section~\ref{subsec:colorphot}). The transit depths did not
significantly change between different bandpasses.
Our assumption in the false-positive probability calculation
(Section~\ref{subsec:fpp}) of no odd-even variations was tested by
independently fitting all odd and all even transits separately.
The resulting best-fit depths were consistent within 1-$\sigma$.
% odd: (Rp/R*)^2 = 0.005500 +0.000558 -0.000169
% even: (Rp/R*)^2 = 0.005659 +0.000636 -0.000185

The posteriors from fitting the TESS data alone are given in
Table~\ref{tab:posterior}.  The condition for a grazing transit is
whether the impact parameter $b$ is below $1 - R_{\rm p}/R_\star$.
The relevant posterior probabilities are shown in
Figure~\ref{fig:subsetcorner}.  The transit is either
grazing, or nearly grazing.  From experimenting with the priors, we
found that in the absence of a strong prior on the stellar density,
the inherent degeneracy between the impact parameter and
planet-to-star size ratio would have been much stronger.  In the
absence of precise information about the star, a larger fraction of
the posterior would therefore have been grazing.  However, our priors
on the stellar parameters from the cluster isochrone fit break this
degeneracy, enabling us to report two-sided limits on the
planet-to-star size ratio.

@@

While we have statistically validated that \tn\ is a planet, the
possibility that it could be a background eclipsing binary has not
been excluded with sufficient confidence to call the planet
``confirmed''.  The distinction is methodological.  Our calculations
have shown that at a population level we expect negligibly few BEBs
within $\approx0.3''$ of \tn\ to produce eclipses of the appropriate
shape across all bandpasses, with no observed secondary eclipse or
odd-even variations.  This statement is
tautologically ``validation'', but it is weaker than having data on
hand that conclusively rules in favor of the planetary interpretation.
